Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-02-28 src/tex/ms.tex
minor wording

% Violin plot
We present the result of our catalog analysis in Fig.~\ref{fig:violin_kappa}.
This shows the posterior distribution on $\kappa$ (abscissa) obtained for each event (ordinate), colored by the distance of the respective posterior mean from the origin in units of standard deviation, i.e., $|\mu/\sigma|$.
The collective measurement obtained by assuming a shared $\kappa$ across events, Eq.~\eqref{eq:restricted_posterior}, is represented by its 90\%-credible symmetric interval (blue band) around the median (blue line);
this joint measurement is fully consistent with $\kappa = 0$ (dashed line), meaning we find no evidence for birefringence.

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}.
\begin{table}
    \caption{Events that best constrain $\kappa$.}
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

The event that shows the largest tension with $\kappa = 0$ is GW170818, for which $|\mu / \sigma| =$ \variable{output/GW170818_constraint.txt}.
Additionally, the GW200129 result shows features that could be indicative of contamination from non-Gaussian instrumental noise.
We discuss both of these events in detail below.

@@

Figure \ref{fig:violin_kappa} shows a degree of variance in the distribution of $\kappa$ posteriors for different events, including some apparent outliers like GW170818.
This is not unexpected: assuming independent Gaussian noise for each event, we might expect up to ${\sim}3$ out of the 71 posteriors (i.e., ${\sim}5\%$) to deviate away from the true $\kappa$ value by over ${\sim}2\sigma$.

>>>>

% Violin plot
Figure \ref{fig:violin_kappa} shows the main result of our GWTC-3 analysis.
as represented by the posterior distribution on $\kappa$ (abscissa) obtained for each event (ordinate), colored by the distance of the respective posterior mean from the origin in units of standard deviation, i.e., $|\mu/\sigma|$.
The collective measurement obtained by assuming a shared $\kappa$ across events, Eq.~\eqref{eq:restricted_posterior}, is represented by its 90\%-credible symmetric interval (blue band) around the median (blue line);
this joint measurement is fully consistent with $\kappa = 0$ (dashed line), meaning we find no evidence for birefringence.

Figure \ref{fig:violin_kappa} makes it clear that not all \acp{BBH} in GWTC-3 are equally informative about birefringence.
When considered individually, the events that best constrain $\kappa$ are listed in Table~\ref{tab:best_events_kappa}.

\begin{table}
    \caption{Events that best constrain $\kappa$.}
    \begin{ruledtabular}
        \variable{output/best_events_kappa.txt}
    \end{ruledtabular}
    \label{tab:best_events_kappa}
\end{table}

The event that shows the largest tension with $\kappa = 0$ is GW170818, for which $|\mu / \sigma| =$ \variable{output/GW170818_constraint.txt}.
\mi{THOMAS: we don't need that many significant figures, $2.0$ would do}
Additionally, the GW200129 result shows features that could be indicative of contamination from non-Gaussian instrumental noise.
We discuss both of these events in detail below.

@@

Figure \ref{fig:violin_kappa} shows a degree of variance in the distribution of $\kappa$ posteriors for different events, including some apparent outliers like GW170818.
This is not unexpected: assuming independent Gaussian noise instantiations for each event, we might expect up to ${\sim}3$ out of the 71 posteriors (i.e., ${\sim}5\%$) to deviate away from the true $\kappa$ value by over ${\sim}2\sigma$.
